---
title: "Hydroxyurea Treatment Summary"
format: 
  html:
    toc: true
    toc-location: left
    html-table-processing: none
    embed-resources: true
---
```{r setup, include=FALSE}

library(squba.gen)
library(squba)
library(gtsummary)
library(gt)
library(patchwork)
library(ggiraph)
library(ggplot2)
library(srcr)
library(stringr)
library(dplyr)

setwd(here::here())
source('setup/argos_wrapper.R')

trino_session <- initialize_session(session_name = 'ssdqa_trino',
                                    db_conn = '.config_files/argos_trino_v57.json',
                                    is_json = TRUE,
                                    cdm_schema = 'ssdqa_paper3',
                                    results_schema = 'ssdqa_paper3', 
                                    vocabulary_schema = 'v57_vocabulary',
                                    retain_intermediates = TRUE,
                                    db_trace = TRUE,
                                    results_tag = '')

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

set_argos_default(trino_session)

```

```{r, include=FALSE}

treated_props <- results_tbl('hu_visits_labelled') %>%
  filter(hu_label != 'censored',
         visit_concept_id %in% c(9201, 9202, 581399, 9203, 2000000048,
                                 2000000088)) %>%
  group_by(site, person_id, hu_label) %>%
  summarise(nvis = n_distinct(visit_occurrence_id)) %>%
  group_by(site, person_id) %>%
  mutate(totvis = sum(nvis),
         propvis = as.numeric(nvis) / as.numeric(totvis)) %>%
  collect()

half_treat <- treated_props %>%
  filter(hu_label == 'hydroxyurea') %>%
  filter(propvis >= 0.5) %>%
  group_by(site) %>%
  summarise(`50pct_pt` = n_distinct(person_id))

sensitivity_treat <- treated_props %>%
  filter(hu_label == 'hydroxyurea') %>%
  filter(propvis >= 0.8) %>%
  group_by(site) %>%
  summarise(`80pct_pt` = n_distinct(person_id))

summ_treat <- results_tbl('final_cohort_censored') %>%
  collect() %>%
  group_by(site) %>%
  summarise(tot_pt = n_distinct(person_id)) %>%
  left_join(half_treat) %>%
  left_join(sensitivity_treat) %>%
  mutate(`80pct_pt` = ifelse(is.na(`80pct_pt`), 0, `80pct_pt`)) %>%
  mutate(prop50 = as.numeric(`50pct_pt`) / as.numeric(tot_pt),
         prop80 = as.numeric(`80pct_pt`) / as.numeric(tot_pt))

summ_treat_hu <- cdm_tbl('de_hydroxyurea') %>%
  inner_join(results_tbl('final_cohort_censored')) %>%
  group_by(site) %>%
  summarise(tot_pt = n_distinct(person_id)) %>%
  collect() %>%
  left_join(half_treat) %>%
  left_join(sensitivity_treat) %>%
  mutate(`80pct_pt` = ifelse(is.na(`80pct_pt`), 0, `80pct_pt`)) %>%
  mutate(prop50 = as.numeric(`50pct_pt`) / as.numeric(tot_pt),
         prop80 = as.numeric(`80pct_pt`) / as.numeric(tot_pt))

```

## Distribution of Visit Types

Classification of all visits after the patient's first SCA diagnosis

:::{.panel-tabset}

# Treated Visits
```{r}

treated_props %>%
  filter(hu_label == 'hydroxyurea') %>%
  ggplot(aes(x = propvis)) +
  geom_histogram(binwidth = 0.1) +
  facet_wrap(~site, scales = 'free_y', nrow = 4) +
  theme_bw()

```

# Untreated Visits
```{r}

treated_props %>%
  filter(hu_label == 'no hydroxyurea') %>%
  ggplot(aes(x = propvis)) +
  geom_histogram(binwidth = 0.1) +
  facet_wrap(~site, scales = 'free_y', nrow = 4) +
  theme_bw()

```

:::

# Treated Patients (50%)

## Out of all patients

```{r}

summ_treat %>%
  mutate(site = paste0(site, '\nTotal N: ', tot_pt)) %>%
  ggplot(aes(y = site, x = prop50, fill = site)) +
  geom_col(show.legend = FALSE) +
  ggsci::scale_fill_igv() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  labs(x = 'Prop. Patients with 50%+ of Visits \n on Hydroxyurea')

```

## Out of hydroxurea exposed patients

```{r}

summ_treat_hu %>%
  mutate(site = paste0(site, '\nTotal N: ', tot_pt)) %>%
  ggplot(aes(y = site, x = prop50, fill = site)) +
  geom_col(show.legend = FALSE) +
  ggsci::scale_fill_igv() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  labs(x = 'Prop. Patients with 50%+ of Visits \n on Hydroxyurea')

```

# Treated Patients (80%)

## Out of all patients

```{r}

summ_treat %>%
  mutate(site = paste0(site, '\nTotal N: ', tot_pt)) %>%
  ggplot(aes(y = site, x = prop80, fill = site)) +
  geom_col(show.legend = FALSE) +
  ggsci::scale_fill_igv() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  labs(x = 'Prop. Patients with 80%+ of Visits \n on Hydroxyurea')

```

## Out of hydroxyurea treated patients

```{r}

summ_treat_hu %>%
  mutate(site = paste0(site, '\nTotal N: ', tot_pt)) %>%
  ggplot(aes(y = site, x = prop80, fill = site)) +
  geom_col(show.legend = FALSE) +
  ggsci::scale_fill_igv() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  labs(x = 'Prop. Patients with 80%+ of Visits \n on Hydroxyurea')

```

# Length of Prescription

## Pre-Normalization

```{r}

results_tbl('de_hydroxyurea_windows') %>%
  ggplot(aes(x = length_rx, y = site)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = 'Length of Prescription')

```

## Post-Normalization
```{r}

results_tbl('de_hydroxyurea_windows') %>%
  ggplot(aes(x = days_supply, y = site)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = 'Length of Prescription')

```

# Time Between Visits (Face to Face Only)

## Overall (All)
```{r}

time_bw_vis <- results_tbl('hu_visits_labelled') %>%
  filter(hu_label != 'censored',
         visit_concept_id %in% c(9201, 9202, 581399, 9203, 2000000048,
                                 2000000088)) %>%
  left_join(cdm_tbl('cdm_person') %>% select(person_id, birth_date)) %>%
  arrange(site, person_id, visit_start_date) %>%
  group_by(site, person_id) %>%
  #filter(visit_concept_id %in% c(9201, 9202, 9203)) %>%
  mutate(time_bw_visits = date_diff('day', lag(visit_end_date), 
                                    visit_start_date)) %>% collect()

time_bw_vis %>%
  ggplot(aes(x = time_bw_visits, y = site)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = 'Time between Visits')

```

## Overall (only above 0)
```{r}
time_bw_vis %>%
  filter(time_bw_visits > 0) %>%
  ggplot(aes(x = time_bw_visits, y = site)) +
  geom_boxplot(outliers = TRUE) +
  theme_bw() +
  labs(x = 'Time between Visits')
```

```{r}
time_bw_vis %>%
  filter(time_bw_visits > 0) %>%
  ggplot(aes(x = time_bw_visits, y = site)) +
  geom_boxplot(outliers = FALSE) +
  theme_bw() +
  labs(x = 'Time between Visits')
```

## Per Patient (all)
```{r}

time_bw_vis %>%
  #filter(visit_concept_id %in% c(9201, 9202, 9203)) %>%
  group_by(site, person_id) %>%
  summarise(med_time_bw = median(time_bw_visits, na.rm = TRUE)) %>%
  group_by(site) %>%
  summarise(med_time_bw2 = median(med_time_bw, na.rm = TRUE),
            q1_time_bw = quantile(med_time_bw, 0.25, na.rm = TRUE),
            q3_time_bw = quantile(med_time_bw, 0.75, na.rm = TRUE)) %>%
  ggplot(aes(y = site)) +
  geom_linerange(aes(xmin = q1_time_bw, xmax = q3_time_bw)) +
  geom_point(aes(x = med_time_bw2)) +
  theme_bw() +
  ggtitle('Median of the Median Days between Visits per Patient') +
  labs(x = 'Time between Visits')

```

## Per Patient (only above 0)
```{r}

time_bw_vis %>%
  #filter(visit_concept_id %in% c(9201, 9202, 9203)) %>%
  filter(time_bw_visits > 0) %>%
  group_by(site, person_id) %>%
  summarise(med_time_bw = median(time_bw_visits, na.rm = TRUE)) %>%
  group_by(site) %>%
  summarise(med_time_bw2 = median(med_time_bw, na.rm = TRUE),
            q1_time_bw = quantile(med_time_bw, 0.25, na.rm = TRUE),
            q3_time_bw = quantile(med_time_bw, 0.75, na.rm = TRUE)) %>%
  ggplot(aes(y = site)) +
  geom_linerange(aes(xmin = q1_time_bw, xmax = q3_time_bw)) +
  geom_point(aes(x = med_time_bw2)) +
  theme_bw() +
  ggtitle('Median of the Median Days between Visits per Patient') +
  labs(x = 'Time between Visits')

```


# Age-Year Computation
```{r, include=FALSE}

ay_test <- results_tbl('hu_visits_labelled') %>%
  filter(hu_label != 'censored',
         visit_concept_id %in% c(9201, 9202, 581399, 9203, 2000000048,
                                 2000000088)) %>%
  left_join(cdm_tbl('cdm_person') %>% select(person_id, birth_date)) %>%
  mutate(visit_age = date_diff('day', birth_date, visit_start_date),
         age_year = floor(visit_age / 365.25),
         age_year = as.numeric(age_year)) %>%
  group_by(site, person_id, age_year, hu_label) %>%
  summarise(nvis = n_distinct(visit_occurrence_id)) %>%
  group_by(site, person_id, age_year) %>%
  mutate(totvis = sum(nvis),
         propvis = as.numeric(nvis) / as.numeric(totvis)) %>%
  collect()

half_treat <- ay_test %>%
  filter(hu_label == 'hydroxyurea') %>%
  filter(propvis >= 0.5) %>%
  group_by(site, age_year) %>%
  summarise(`50pct_pt` = n_distinct(person_id))

sensitivity_treat <- ay_test %>%
  filter(hu_label == 'hydroxyurea') %>%
  filter(propvis >= 0.8) %>%
  group_by(site, age_year) %>%
  summarise(`80pct_pt` = n_distinct(person_id))

summ_treat <- ay_test %>%
  collect() %>%
  group_by(site, age_year) %>%
  summarise(tot_pt = n_distinct(person_id)) %>%
  left_join(half_treat) %>%
  left_join(sensitivity_treat) %>%
  mutate(`80pct_pt` = ifelse(is.na(`80pct_pt`), 0, `80pct_pt`)) %>%
  mutate(prop50 = as.numeric(`50pct_pt`) / as.numeric(tot_pt),
         prop80 = as.numeric(`80pct_pt`) / as.numeric(tot_pt))

summ_treat_hu <- cdm_tbl('de_hydroxyurea') %>%
  collect() %>%
  inner_join(ay_test) %>%
  group_by(site, age_year) %>%
  summarise(tot_pt = n_distinct(person_id)) %>%
  collect() %>%
  left_join(half_treat) %>%
  left_join(sensitivity_treat) %>%
  mutate(`80pct_pt` = ifelse(is.na(`80pct_pt`), 0, `80pct_pt`)) %>%
  mutate(prop50 = as.numeric(`50pct_pt`) / as.numeric(tot_pt),
         prop80 = as.numeric(`80pct_pt`) / as.numeric(tot_pt))

```

## Out of all patients

- Numerator is patients with at least 50% of visits with hydroxyurea in that age year
- Denominator is patients with at least one visit in that age year
```{r}
plt <- summ_treat %>%
  mutate(tooltip = paste0('Prop. = ', round(prop50, 2),
                          '\nCount = ', `50pct_pt`,
                          '\n Age Year = ', age_year)) %>%
  ggplot(aes(x = age_year, y = prop50, color = site)) +
  geom_line() +
  geom_point(aes(text = tooltip)) +
  theme_bw() +
  scale_x_continuous(limits = c(-1,26), expand = c(0, 0)) +
  labs(x = 'Age-Year',
       y = 'Prop. Patients with 50%+ of Visits \n on Hydroxyurea')

plotly::ggplotly(plt, tooltip = 'text')
```

## Out of hydroxyurea treated patients

Patients with at least one exposure to hydroxyurea all-time

- Numerator is patients with at least 50% of visits with hydroxyurea in that age year
- Denominator is patients with at least one visit in that age year
```{r}

plt <- summ_treat_hu %>%
  mutate(tooltip = paste0('Prop. = ', round(prop50, 2),
                          '\nCount = ', `50pct_pt`,
                          '\n Age Year = ', age_year)) %>%
  ggplot(aes(x = age_year, y = prop50, color = site)) +
  geom_line() +
  geom_point(aes(text = tooltip)) +
  theme_bw() +
  scale_x_continuous(limits = c(-1,26), expand = c(0, 0)) +
  labs(x = 'Age-Year',
       y = 'Prop. Patients with 50%+ of Visits \n on Hydroxyurea')

plotly::ggplotly(plt, tooltip = 'text')

```
