---
title: "DID Analysis Comparison: Pre & Post DQ Intervention"
format: 
  html:
    embed-resources: true
    html-table-processing: none
    toc: true
---

```{r setup, include=FALSE}

library(squba.gen)
library(squba)
library(gtsummary)
library(gt)
library(patchwork)
library(ggiraph)
library(ggplot2)
library(did)

setwd(here::here())
source('setup/setup.R')


get_results <- function(dat){
  
  results_tbl(dat) %>% collect()
}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

set_argos_default(trino_session)

combo_tbl <- results_tbl('did_primary_vars') %>%
  mutate(cohort = 'SQUBA') %>%
  union(results_tbl('did_primary_vars_nodq') %>% mutate(cohort = 'Non-SQUBA')) %>%
  collect()


did_plts <- function(did_dat,
                     ylab,
                     model_name = 'All Patients'){
  
  agg.es <- aggte(did_dat, type = "dynamic", na.rm = TRUE)

  model_name <- model_name
  outcome <- agg.es$DIDparams$yname
  ATT <- agg.es$overall.att
  standard_error <- agg.es$overall.se
  CI_low <- ATT - qt(0.975, df = Inf) * standard_error
  CI_high <- ATT + qt(0.975, df = Inf) * standard_error

  tb <- tibble(model_name = model_name,
         outcome = outcome,
         ATT = ATT,
         standard_error = standard_error,
         CI_low = CI_low,
         CI_high = CI_high) %>%
    gt::gt() %>%
    gt::tab_header('Overall Summary')

  coef.cs <- tidy(agg.es)
  coef.cs$period <- ifelse(coef.cs$event.time < 0, "Pre-treatment", "Post-treatment")

  # Custom event study plot (ED_days_per_year)
  plt <- ggplot(coef.cs %>% filter(event.time > -6 & event.time < 11), 
         aes(x = event.time, y = estimate, color = period)) + 
    geom_point() + 
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) + 
    geom_hline(yintercept = 0, linetype = "dotted") + 
    geom_vline(xintercept = 0, linetype = "dashed", color = "red") + 
    scale_color_manual(values = c("Pre-treatment" = "darkred", "Post-treatment" = "darkblue")) + 
    labs(title = "Event Study Estimates", 
         subtitle = model_name,
         x = "Treatment year (0 = hydroxyurea initiation)", 
         y = ylab, 
         color = "Period") + 
    theme_classic()
  
  opt <- list(tb, plt)
  
  return(opt)
}

```

## Cohort Comparison
```{r, fig.height=8}

plt <- ssc_output(process_output = get_results('ssc_ms_exp_cs_dqcomp'),
           alt_cohort_filter = c('Non-SQUBA', 'SQUBA Treated Adherent'))

plt[[1]]$data <- plt[[1]]$data %>% mutate(cohort_id = case_when(cohort_id == 'Base Cohort' ~ 'SQUBA', grepl('Non-SQUBA', cohort_id) ~ 'Non-SQUBA', TRUE ~ 'SQUBA Treated \nAdherent'),
                                          cohort_id = factor(cohort_id, levels = c('Non-SQUBA', 'SQUBA', 'SQUBA Treated \nAdherent')))
plt[[1]] <- plt[[1]] + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
make_interactive_squba(plt[[1]])
plt[[2]]$data <- plt[[2]]$data %>% mutate(cohort_id = case_when(cohort_id == 'Base Cohort' ~ 'SQUBA', grepl('Non-SQUBA', cohort_id) ~ 'Non-SQUBA', TRUE ~ 'SQUBA Treated \nAdherent'),
                                          cohort_id = factor(cohort_id, levels = c('Non-SQUBA', 'SQUBA', 'SQUBA Treated \nAdherent')))
plt[[2]] <- plt[[2]] + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
make_interactive_squba(plt[[2]])

```

### Tabular SSC Output
:::{.panel-tabset}
# SQUBA Cohort
```{r}

get_results('ssc_ms_exp_cs_dqcomp') %>%
  filter(cohort_id == 'base_cohort') %>%
  select(site, cohort_characteristic, fact_group, fact_summary, cohort_total_pt) %>%
  mutate(site_lab = paste0(site, '\n(N = ', cohort_total_pt, ')')) %>%
  select(-c(site, cohort_total_pt)) %>% 
  pivot_wider(names_from = site_lab,
              values_from = fact_summary) %>%
  gt(groupname_col = 'fact_group') %>%
  fmt_number() %>%
  fmt_percent(rows = grepl('prop', cohort_characteristic)) %>%
  opt_stylize()
  

```

# Non-SQUBA Cohort
```{r}

get_results('ssc_ms_exp_cs_dqcomp') %>%
  filter(grepl('Non-SQUBA', cohort_id)) %>%
  select(site, cohort_characteristic, fact_group, fact_summary, cohort_total_pt) %>%
  mutate(site_lab = paste0(site, '\n(N = ', cohort_total_pt, ')')) %>%
  select(-c(site, cohort_total_pt)) %>% 
  pivot_wider(names_from = site_lab,
              values_from = fact_summary) %>%
  gt(groupname_col = 'fact_group') %>%
  fmt_number() %>%
  fmt_percent(rows = grepl('prop', cohort_characteristic)) %>%
  opt_stylize()
  

```

# SQUBA Treated Adherent
```{r}

get_results('ssc_ms_exp_cs_dqcomp') %>%
  filter(grepl('Adherent', cohort_id)) %>%
  select(site, cohort_characteristic, fact_group, fact_summary, cohort_total_pt) %>%
  mutate(site_lab = paste0(site, '\n(N = ', cohort_total_pt, ')')) %>%
  select(-c(site, cohort_total_pt)) %>% 
  pivot_wider(names_from = site_lab,
              values_from = fact_summary) %>%
  gt(groupname_col = 'fact_group') %>%
  fmt_number() %>%
  fmt_percent(rows = grepl('prop', cohort_characteristic)) %>%
  opt_stylize()
  

```
:::

## Exploratory Viz

### Average MCV per Age Year
```{r}

combo_tbl %>%
  ggplot(aes(x = avg_mcv, fill = cohort)) +
  geom_density(alpha = 0.5) + 
  labs(title = "Density Plot for MCV",
       x = "Average MCV",
       y = "Density") +
  theme_minimal()

```

```{r, fig.width=8}

my_dat <- combo_tbl %>%
  filter(age_year >= 0) %>%
  group_by(site, age_year, avg_mcv, cohort) %>%
  summarise(npt = n_distinct(person_id)) %>%
  group_by(age_year) %>%
  mutate(tot_pt = sum(npt)) %>%
  filter(is.na(avg_mcv)) %>%
  mutate(prop_na = as.numeric(npt) / as.numeric(tot_pt)) 

my_dat %>%
  ggplot(aes(x = age_year, y = prop_na)) +
  geom_col(aes(fill = site)) +
  facet_wrap(~cohort) +
  # geom_label(data = my_dat %>%
  #              group_by(cohort) %>%
  #              mutate(prop_na = sum(prop_na)) %>%
  #              distinct(age_year, tot_pt, prop_na),
  #            aes(label = tot_pt), size = 2) +
  theme_minimal() +
  labs(title = 'Patients Missing Measurements per Age Year')

```

### Average ANC per Age Year
```{r}

combo_tbl %>%
  ggplot(aes(x = avg_anc, fill = cohort)) +
  geom_density(alpha = 0.5) + 
  labs(title = "Density Plot for ANC",
       x = "Average ANC",
       y = "Density") +
  theme_minimal()

```

```{r, fig.width=8}

my_dat <- combo_tbl %>%
  filter(age_year >= 0) %>%
  group_by(site, age_year, avg_anc, cohort) %>%
  summarise(npt = n_distinct(person_id)) %>%
  group_by(age_year) %>%
  mutate(tot_pt = sum(npt)) %>%
  filter(is.na(avg_anc)) %>%
  mutate(prop_na = as.numeric(npt) / as.numeric(tot_pt)) 

my_dat %>%
  ggplot(aes(x = age_year, y = prop_na)) +
  geom_col(aes(fill = site)) +
  facet_wrap(~cohort) +
  # geom_label(data = my_dat %>%
  #              mutate(prop_na = sum(prop_na)) %>%
  #              distinct(age_year, tot_pt, prop_na),
  #            aes(label = tot_pt), size = 2) +
  theme_minimal() +
  labs(title = 'Patients Missing Measurements per Age Year')

```

### Average Hemoglobin per Age Year
```{r}

combo_tbl %>%
  ggplot(aes(x = avg_hgb, fill = cohort)) +
  geom_density(alpha = 0.5) +  
  labs(title = "Density Plot for Hgb",
       x = "Average Hgb",
       y = "Density") +
  theme_minimal()

```

```{r, fig.width=8}

my_dat <- combo_tbl %>%
  filter(age_year >= 0) %>%
  group_by(site, age_year, avg_hgb, cohort) %>%
  summarise(npt = n_distinct(person_id)) %>%
  group_by(age_year) %>%
  mutate(tot_pt = sum(npt)) %>%
  filter(is.na(avg_hgb)) %>%
  mutate(prop_na = as.numeric(npt) / as.numeric(tot_pt)) 

my_dat %>%
  ggplot(aes(x = age_year, y = prop_na)) +
  geom_col(aes(fill = site)) +
  facet_wrap(~cohort) +
  # geom_label(data = my_dat %>%
  #              mutate(prop_na = sum(prop_na)) %>%
  #              distinct(age_year, tot_pt, prop_na),
  #            aes(label = tot_pt), size = 2) +
  theme_minimal() +
  labs(title = 'Patients Missing Measurements per Age Year')

```

### Total ED Visits per Age Year
```{r}

combo_tbl %>%
  #filter(ed_days_ageyear < 20) %>%
  ggplot(aes(x = ed_vis_ageyear)) +
  geom_histogram(fill = "blue", alpha = 0.5,
                 binwidth = 1) +  
  facet_wrap(~cohort) +
  labs(title = "Density Plot for ED Days",
       x = "ED Days",
       y = "Density") +
  theme_minimal()

```

```{r}

combo_tbl %>%
  filter(ed_days_ageyear < 20) %>%
  ggplot(aes(x = ed_days_ageyear)) +
  geom_histogram(fill = "blue", alpha = 0.5,
                 binwidth = 1) +  
  facet_wrap(~cohort) +
  labs(title = "Density Plot for ED Days (Drop Extremes)",
       x = "ED Days",
       y = "Density") +
  theme_minimal()

```

```{r, fig.width=8}

my_dat <- combo_tbl %>%
  filter(age_year >= 0) %>%
  group_by(site, age_year, ed_days_ageyear, cohort) %>%
  summarise(npt = n_distinct(person_id)) %>%
  group_by(age_year) %>%
  mutate(tot_pt = sum(npt)) %>%
  filter(is.na(ed_days_ageyear)) %>%
  mutate(prop_na = as.numeric(npt) / as.numeric(tot_pt)) 

my_dat %>%
  ggplot(aes(x = age_year, y = prop_na)) +
  geom_col(aes(fill = site)) +
  # geom_label(data = my_dat %>%
  #              mutate(prop_na = sum(prop_na)) %>%
  #              distinct(age_year, tot_pt, prop_na),
  #            aes(label = tot_pt), size = 2) +
  facet_wrap(~cohort) +
  theme_minimal() +
  labs(title = 'Patients Missing Measurements per Age Year')

```

### Total Hospitalized Days per Age Year
```{r}

combo_tbl %>%
  filter(hosp_days_ageyear >= 0) %>%
  ggplot(aes(x = hosp_days_ageyear)) +
  geom_histogram(fill = "blue", alpha = 0.5,
                 binwidth = 1) +  
  facet_wrap(~cohort) +
  labs(title = "Density Plot for IP Days",
       x = "IP Days",
       y = "Density") +
  theme_minimal()

```

```{r}

combo_tbl %>%
  filter(hosp_days_ageyear >= 0 & hosp_days_ageyear < 50) %>%
  ggplot(aes(x = hosp_days_ageyear)) +
  geom_histogram(fill = "blue", alpha = 0.5,
                 binwidth = 1) +  
  facet_wrap(~cohort) +
  labs(title = "Density Plot for IP Days (Drop Extremes)",
       x = "IP Days",
       y = "Density") +
  theme_minimal()

```

```{r, fig.width=8}

my_dat <- combo_tbl %>%
  filter(age_year >= 0) %>%
  group_by(site, age_year, hosp_days_ageyear, cohort) %>%
  summarise(npt = n_distinct(person_id)) %>%
  group_by(age_year) %>%
  mutate(tot_pt = sum(npt)) %>%
  filter(is.na(hosp_days_ageyear)) %>%
  mutate(prop_na = as.numeric(npt) / as.numeric(tot_pt)) 

my_dat %>%
  ggplot(aes(x = age_year, y = prop_na)) +
  geom_col(aes(fill = site)) +
  # geom_label(data = my_dat %>%
  #              mutate(prop_na = sum(prop_na)) %>%
  #              distinct(age_year, tot_pt, prop_na),
  #            aes(label = tot_pt), size = 2) +
  facet_wrap(~cohort) +
  theme_minimal() +
  labs(title = 'Patients Missing Measurements per Age Year')

```

### Missingness by Lab
#### SQUBA Cohort
```{r}

my_dat <- combo_tbl %>%
  filter(age_year >= 0) %>%
  collect() %>%
  mutate(missing_mcv = ifelse(is.na(avg_mcv), 'mcv', NA),
         missing_hgb = ifelse(is.na(avg_hgb), 'hgb', NA),
         missing_anc = ifelse(is.na(avg_anc), 'anc', NA),
         missing_labs = paste(missing_mcv, missing_anc, 
                              missing_hgb),
         missing_labs = str_replace_all(missing_labs, 'NA', ''),
         missing_labs = trimws(missing_labs),
         missing_labs = ifelse(missing_labs == '', 'none', 
                               missing_labs)) %>%
  group_by(site, age_year, missing_labs, cohort) %>%
  summarise(n_pt = n_distinct(person_id)) %>%
  group_by(site, age_year, cohort) %>%
  mutate(tot_pt = sum(n_pt),
         prop_pt = n_pt / tot_pt) 


plt <- my_dat %>%
  filter(cohort == 'SQUBA') %>%
  ggplot(aes(x = age_year, y = prop_pt, color = missing_labs)) +
  geom_line() +
  facet_wrap(~site) +
  theme_minimal() +
  labs(y = 'Prop. Patients',
       x = 'Age Year',
       color = 'Missing Lab(s)')

plotly::ggplotly(plt)

```

#### Non-SQUBA Cohort
```{r}

plt <- my_dat %>%
  filter(cohort != 'SQUBA') %>%
  ggplot(aes(x = age_year, y = prop_pt, color = missing_labs)) +
  geom_line() +
  facet_wrap(~site) +
  theme_minimal() +
  labs(y = 'Prop. Patients',
       x = 'Age Year',
       color = 'Missing Lab(s)')

plotly::ggplotly(plt)

```

## DID Analysis
```{r}
# Create a modified data frame with treatment variables for CS estimation
df_CS <- results_tbl('did_primary_vars') %>% 
  collect() %>%
  group_by(site, person_id) %>%
  mutate(age_year_first_hu = case_when(any(treated_50 == 1) ~ age_year_first_hu + 1,
                                       TRUE ~ NA_integer_)) %>%
  ungroup() %>%
  mutate(
    first_HU_age_CS = if_else(is.na(age_year_first_hu), 0, age_year_first_hu), 
    first_HU_calendar_year_CS = if_else(is.na(age_year_first_hu), 0, calendar_year_first_hu)
  )

df_CS_nodq <- results_tbl('did_primary_vars_nodq') %>% 
  collect() %>%
  group_by(site, person_id) %>%
  mutate(age_year_first_hu = case_when(any(treated_50 == 1) ~ age_year_first_hu + 1,
                                       TRUE ~ NA_integer_)) %>%
  ungroup() %>%
  mutate(
    first_HU_age_CS = if_else(is.na(age_year_first_hu), 0, age_year_first_hu), 
    first_HU_calendar_year_CS = if_else(is.na(age_year_first_hu), 0, calendar_year_first_hu)
  )
```

### ED Visits
#### SQUBA Cohort
```{r}

#### ED days
df_ed <- df_CS %>%
  mutate(ed_vis_ageyear = ifelse(is.na(ed_vis_ageyear), 0, ed_vis_ageyear)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "ed_vis_ageyear",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_ed, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in ED visits per year')
plts[[1]]
plts[[2]] + ylim(-2, 0.75)

ggsave('../results/figure2b_squba_ed.png',
       plts[[2]] + 
         ylim(-2, 0.75) + 
         ggtitle('DFE Cohort') +
         theme(legend.position = 'bottom',
               #plot.title = element_blank(),
               plot.subtitle = element_blank(),
               text = element_text(size = 12)),
       height = 7,
       width = 7,
       dpi = 300)

```

#### Non-SQUBA Cohort
```{r}

#### ED days
df_ed <- df_CS_nodq %>%
  mutate(ed_vis_ageyear = ifelse(is.na(ed_vis_ageyear), 0, ed_vis_ageyear)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "ed_vis_ageyear",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_ed, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in ED visits per year')
plts[[1]]
plts[[2]] + ylim(-2, 0.75)

ggsave('../results/figure2c_asis_ed.png',
       plts[[2]] + 
         ylim(-2, 0.75) + 
         ggtitle('AS-IS Cohort') +
         theme(legend.position = 'bottom',
               #plot.title = element_blank(),
               plot.subtitle = element_blank(),
               text = element_text(size = 12)),
       height = 7,
       width = 7,
       dpi = 300)

```

### Hospitalization Days
#### SQUBA Cohort
```{r}

#### ED days
df_hosp <- df_CS %>%
  mutate(hosp_days_ageyear = ifelse(is.na(hosp_days_ageyear), 0, hosp_days_ageyear)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "hosp_days_ageyear",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hosp, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in Hospitalization days per year')
plts[[1]]
plts[[2]]

```

#### Non-SQUBA Cohort
```{r}

#### ED days
df_hosp <- df_CS_nodq %>%
  mutate(hosp_days_ageyear = ifelse(is.na(hosp_days_ageyear), 0, hosp_days_ageyear)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "hosp_days_ageyear",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hosp, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in Hospitalization days per year')
plts[[1]]
plts[[2]]

```

### Hospitalization Visits
#### SQUBA Cohort
```{r}

#### ED days
df_hosp <- df_CS %>%
  mutate(hosp_vis_ageyear = ifelse(is.na(hosp_vis_ageyear), 0, hosp_vis_ageyear)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "hosp_vis_ageyear",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hosp, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in Hospitalization visits per year')
plts[[1]]
plts[[2]]

```

#### Non-SQUBA Cohort
```{r}

#### ED days
df_hosp <- df_CS_nodq %>%
  mutate(hosp_vis_ageyear = ifelse(is.na(hosp_vis_ageyear), 0, hosp_vis_ageyear)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "hosp_vis_ageyear",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hosp, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in Hospitalization visits per year')
plts[[1]]
plts[[2]]
```


### Hemoglobin Labs
#### SQUBA Cohort
```{r}

#### ED days
df_hgb <- df_CS %>%
  filter(site == 'nemours') %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "avg_hgb",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hgb, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in hemoglobin average')
plts[[1]]
plts[[2]] + ylim(-0.7, 1.5) 

# ggsave('../results/figure3b_squba_hgb.png',
#        plts[[2]] +
#          ylim(-0.6, 1) +
#          ggtitle('DFE Cohort') +
#          theme(legend.position = 'bottom',
#                #plot.title = element_blank(),
#                plot.subtitle = element_blank(),
#                text = element_text(size = 12)),
#        height = 7,
#        width = 7,
#        dpi = 300)

```

#### Non-SQUBA Cohort
```{r}

#### ED days
df_hgb <- df_CS_nodq %>%
  mutate(avg_hgb = as.numeric(avg_hgb)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "avg_hgb",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hgb, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in Average Hemoglobin per year')
plts[[1]]
plts[[2]]

```


### MCV Labs
#### SQUBA Cohort
```{r}

#### ED days
df_hgb <- df_CS %>%
  #mutate(avg_hgb = ifelse(is.na(avg_hgb), 0, avg_hgb)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "avg_mcv",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hgb, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in Average MCV per year')
plts[[1]]
plts[[2]]

```

#### Non-SQUBA Cohort
```{r}

#### ED days
df_hgb <- df_CS_nodq %>%
  mutate(avg_mcv = as.numeric(avg_mcv)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "avg_mcv",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hgb, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in Average MCV per year')
plts[[1]]
plts[[2]]

```

### ANC Labs
#### SQUBA Cohort
```{r}

#### ED days
df_hgb <- df_CS %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "avg_anc",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hgb, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in Average ANC per year')
plts[[1]]
plts[[2]]

```

#### Non-SQUBA Cohort
```{r}

#### ED days
df_hgb <- df_CS_nodq %>%
  mutate(avg_anc = as.numeric(avg_anc)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "avg_anc",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hgb, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in Average ANC per year')
plts[[1]]
plts[[2]]

```

## Sensitivity Analysis - Good Adherence
```{r}
# Create a modified data frame with treatment variables for CS estimation
blah <- results_tbl('did_primary_vars') %>%
  group_by(site, person_id) %>%
  mutate(never_treated = ifelse(any(treated_50 == 1L), FALSE, TRUE),
         yrs_treated = sum(treated_50)) %>%
  #ungroup() %>%
  mutate(mcv_thresh = case_when(age_year < 1 ~ baseline_mcv * 1.1,
                             age_year >= 1 & age_year < 4 ~ 
                               (baseline_mcv * 1.1) + 4,
                             age_year >= 4 ~ (baseline_mcv * 1.1) + 6)) %>%
  mutate(adherant = case_when(never_treated ~ TRUE,
                              avg_mcv >= mcv_thresh ~ TRUE,
                              yrs_treated == 1L ~ TRUE,
                              TRUE ~ FALSE)) %>%
  filter(adherant)

df_CS <- blah %>% 
  collect() %>%
  group_by(site, person_id) %>%
  mutate(age_year_first_hu = case_when(any(treated_50 == 1) ~ age_year_first_hu + 1,
                                       TRUE ~ NA_integer_)) %>%
  ungroup() %>%
  mutate(
    first_HU_age_CS = if_else(is.na(age_year_first_hu), 0, age_year_first_hu), 
    first_HU_calendar_year_CS = if_else(is.na(age_year_first_hu), 0, calendar_year_first_hu)
  ) 
  

blah_nodq <- results_tbl('did_primary_vars_nodq') %>%
  group_by(site, person_id) %>%
  mutate(never_treated = ifelse(any(treated_50 == 1L), FALSE, TRUE),
         yrs_treated = sum(treated_50)) %>%
  #ungroup() %>%
  mutate(mcv_thresh = case_when(age_year < 1 ~ baseline_mcv * 1.1,
                             age_year >= 1 & age_year < 4 ~ 
                               (baseline_mcv * 1.1) + 4,
                             age_year >= 4 ~ (baseline_mcv * 1.1) + 6)) %>%
  mutate(adherant = case_when(never_treated ~ TRUE,
                              avg_mcv >= mcv_thresh ~ TRUE,
                              yrs_treated == 1L ~ TRUE,
                              TRUE ~ FALSE)) %>%
  filter(adherant)
  
df_CS_nodq <- blah_nodq %>% 
  collect() %>%
  group_by(site, person_id) %>%
  mutate(age_year_first_hu = case_when(any(treated_50 == 1) ~ age_year_first_hu + 1,
                                       TRUE ~ NA_integer_)) %>%
  ungroup() %>%
  mutate(
    first_HU_age_CS = if_else(is.na(age_year_first_hu), 0, age_year_first_hu), 
    first_HU_calendar_year_CS = if_else(is.na(age_year_first_hu), 0, calendar_year_first_hu)
  )
```

:::{.callout-note}
Patients are included in this cohort if they were (a) never treated with hydroxyurea (controls), (b) were treated for only one age year, or (c) exhibited an average annual MCV value that was 110% of the baseline MCV value (recorded on the same date or within the year prior to hydroxyurea initiation)
:::

### ED Visits
#### SQUBA Cohort
```{r}

#### ED days
df_ed <- df_CS %>%
  mutate(ed_vis_ageyear = ifelse(is.na(ed_vis_ageyear), 0, ed_vis_ageyear)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "ed_vis_ageyear",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_ed, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in ED visits per year', model_name = 'adherent patients')
plts[[1]]
plts[[2]]

```

#### Non-SQUBA Cohort
```{r}

#### ED days
df_ed <- df_CS_nodq %>%
  mutate(ed_vis_ageyear = ifelse(is.na(ed_vis_ageyear), 0, ed_vis_ageyear)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "ed_vis_ageyear",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_ed, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in ED visits per year', model_name = 'adherent patients')
plts[[1]]
plts[[2]]

```

### Hospitalization Days
#### SQUBA Cohort
```{r}

#### ED days
df_hosp <- df_CS %>%
  mutate(hosp_days_ageyear = ifelse(is.na(hosp_days_ageyear), 0, hosp_days_ageyear)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "hosp_days_ageyear",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hosp, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in Hospitalization days per year', model_name = 'adherent patients')
plts[[1]]
plts[[2]]

```

#### Non-SQUBA Cohort
```{r}

#### ED days
df_hosp <- df_CS_nodq %>%
  mutate(hosp_days_ageyear = ifelse(is.na(hosp_days_ageyear), 0, hosp_days_ageyear)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "hosp_days_ageyear",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hosp, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in Hospitalization days per year', model_name = 'adherent patients')
plts[[1]]
plts[[2]]

```

### Hospitalization Visits
#### SQUBA Cohort
```{r}

#### ED days
df_hosp <- df_CS %>%
  mutate(hosp_vis_ageyear = ifelse(is.na(hosp_vis_ageyear), 0, hosp_vis_ageyear)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "hosp_vis_ageyear",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hosp, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in Hospitalization visits per year', model_name = 'adherent patients')
plts[[1]]
plts[[2]]

```

#### Non-SQUBA Cohort
```{r}

#### ED days
df_hosp <- df_CS_nodq %>%
  mutate(hosp_vis_ageyear = ifelse(is.na(hosp_vis_ageyear), 0, hosp_vis_ageyear)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "hosp_vis_ageyear",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hosp, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in Hospitalization visits per year', model_name = 'adherent patients')
plts[[1]]
plts[[2]]
```


### Hemoglobin Labs
#### SQUBA Cohort
```{r}

#### ED days
df_hgb <- df_CS %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "avg_hgb",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hgb, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in hemoglobin average', model_name = 'adherent patients')
plts[[1]]
plts[[2]] + ylim(-1, 1.5)

ggsave('../results/figure3d_adherent_hgb.png',
       plts[[2]] +
         ylim(-1, 1.5) +
         ggtitle('DFE Adherent Cohort') +
         theme(legend.position = 'bottom',
               #plot.title = element_blank(),
               plot.subtitle = element_blank(),
               text = element_text(size = 12)),
       height = 7,
       width = 7,
       dpi = 300)

```

#### Non-SQUBA Cohort
```{r}

#### ED days
df_hgb <- df_CS_nodq %>%
  mutate(avg_hgb = as.numeric(avg_hgb)) %>%
  filter(age_year >= 0) %>%
  mutate(age_year = age_year + 1)

did1_attgt <- att_gt(
  yname = "avg_hgb",   
  tname = "age_year", 
  idname = "person_id", 
  gname = "first_HU_age_CS", 
  data = df_hgb, 
  # xformla = xformula,  # Uncomment to include covariates
  est_method = "dr", 
  faster_mode = FALSE,
  panel = TRUE, 
  allow_unbalanced_panel = TRUE, 
  control_group = "notyettreated"
)

plts <- did_plts(did_dat = did1_attgt, ylab = 'Change in hemoglobin average', model_name = 'adherent patients')
plts[[1]]
plts[[2]]

ggsave('../results/supp_figure1_asis_adherent_hgb.png',
       plts[[2]] +
         ylim(-1.5, 1.5) +
         ggtitle('AS-IS Adherent Cohort') +
         theme(legend.position = 'bottom',
               #plot.title = element_blank(),
               plot.subtitle = element_blank(),
               text = element_text(size = 12)),
       height = 7,
       width = 7,
       dpi = 300)

```