---
title: "SCA SSDQA Round 6"
format: 
  html:
    toc: true
    toc-location: left
    html-table-processing: none
    embed-resources: true
---

```{r setup, include=FALSE}

library(squba.gen)
library(squba)
library(gtsummary)
library(gt)
library(patchwork)
library(ggiraph)
library(ggplot2)

setwd(here::here())
source('setup/setup.R')

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

set_argos_default(postgres_session)

```

## Source and Concept Vocabularies

### Hemoglobin Labs

Identified relevant source values with the following string search criteria:
 
 - `718-7` (loinc code frequently seen in these source values)
 - `hemoglobin`
 - `total hemoglobin`
 - `cbc` + `hemoglobin`
 - `cbc` + `hgb`
 - `hb tot`

Then, used the identified source values to pull the related codes to try and identify
any potential mismappings or unmapped labs.

```{r}

scv_output(process_output = results_tbl('scv_ms_exp_cs_r6_heme') %>% 
             inner_join(vocabulary_tbl('concept') %>% 
                         select(concept_id, concept_name)) %>% collect(),
           code_type = 'cdm') %>%
  cols_hide('source_concept_name')

```

### ANC Labs
Identified relevant source values with the following string search criteria:

 - `neutrophil`
 - `neutrophils`
 - `absolute neut`
 - NOT `anti-neutrophil`
 - NOT `segmented neutrophil`

Then, used the identified source values to pull the related codes to try and identify
any potential mismappings or unmapped labs.

```{r}

scv_output(process_output = results_tbl('scv_ms_exp_cs_r6_anc') %>% 
             inner_join(vocabulary_tbl('concept') %>% 
                         select(concept_id, concept_name)) %>% collect(),
           code_type = 'cdm') %>%
  cols_hide('source_concept_name')

```

### MCV Labs
Identified relevant source values with the following string search criteria:
 
 - `mcv`
 - `mean corpuscular volume`
 - `mean cell volume`

Then, used the identified source values to pull the related codes to try and identify
any potential mismappings or unmapped labs.

```{r}

scv_output(process_output = results_tbl('scv_ms_exp_cs_r6_mcv') %>%
             inner_join(vocabulary_tbl('concept') %>% 
                         select(concept_id, concept_name)) %>% collect(),
           code_type = 'cdm') %>%
  cols_hide('source_concept_name')

```

### Hydroxyurea
Identified relevant source values with the following string search criteria:

 - `hydroxyurea`
 - `droxia`
 - `siklos`
 - `hydrea`
 - `hydroxyur`

Then, used the identified source values to pull the related codes to try and identify
any potential mismappings or unmapped labs.

```{r}

scv_output(process_output = results_tbl('scv_ms_exp_cs_r6_hdrx') %>%
             inner_join(vocabulary_tbl('concept') %>% 
                         select(concept_id, concept_name)) %>% collect(),
           code_type = 'cdm') %>%
  cols_hide('source_concept_name')

```