---
title: "SCA SSDQA Round 5"
format: 
  html:
    toc: true
    toc-location: left
    html-table-processing: none
    embed-resources: true
---

```{r setup, include=FALSE}

library(squba.gen)
library(squba)
library(gtsummary)
library(gt)
library(patchwork)
library(ggiraph)
library(ggplot2)

setwd(here::here())
source('setup/setup.R')

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

set_argos_default(postgres_session)

```

## Cohort Attrition

Based on the results of previous DQ, we re-ran the attrition to drop any requirement for a lab result of a certain type and just require that a lab was administered. This was done to maximize the patient count and reduce the impact of DQ issues in the results recorded. 

The attrition steps are as follows:
```{r}

tb <- ca_output(process_output = results_tbl('ca_ms_exp_cs_r5') %>% collect(),
                large_n = FALSE)

tb[[2]]

```

### Multi Site, Exploratory, Cross-Sectional

:::{.panel-tabset}

# Number of Patients
```{r}

grph <- ca_output(process_output = results_tbl('ca_ms_exp_cs_r5') %>% collect(),
                  var_col = 'num_pts')

make_interactive_squba(grph[[1]])

```

# Retention
```{r}

grph <- ca_output(process_output = results_tbl('ca_ms_exp_cs_r5') %>% collect(),
                  var_col = 'prop_retained_start')

make_interactive_squba(grph[[1]])

```
:::

### Multi Site, Anomaly Detection, Cross-Sectional
:::{.panel-tabset}

# Number of Patients
```{r}

grph <- ca_output(process_output = results_tbl('ca_ms_anom_cs_num_r5') %>% collect(),
                  var_col = 'num_pts')

make_interactive_squba(grph)

```

# Retention
```{r}

grph <- ca_output(process_output = results_tbl('ca_ms_anom_cs_prs_r5') %>% collect(),
                  var_col = 'prop_retained_start')

make_interactive_squba(grph)

```
:::

## Table 1
```{r}
results_tbl('table1_input_r5') %>%
  collect() %>%
  tbl_summary(by = site, include = -c(person_id, birth_date),
              statistic = c('Follow-Up (Years)' ~ "{mean}")) %>%
  add_overall(last = TRUE) %>%
  bold_labels() %>%
  italicize_levels()
```

## Patient Facts

The hematologist visit category in this check reflects the newly remapped specialties.

The visit type definitions are:
```{r}

read_codeset('input_pf_visits', 'ic') %>% 
  pivot_wider(names_from = visit_type,
              values_from = visit_concept_id) %>%
  select(-c(outpatient, `outpatient (non-9202)`)) %>% 
  mutate(`hematology specialists` = 'any visit_concept_id with a hematology provider or care site specialty') %>%
  mutate(all = 'any visit_concept_id') %>%
  gt::gt() %>%
  tab_header('Visit Type Definitions') %>%
  opt_stylize(style = 2)

```

### Multi Site, Exploratory, Cross-Sectional

:::{.panel-tabset}

# Median with 0s
## All Domains
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_exp_cs_r5') %>% collect(),
          output = 'median_site_with0s')

make_interactive_squba(grph)

```
## Labs + Hydroxyurea
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_exp_cs_r5') %>% collect() %>%
            filter(domain %in% c('anc labs', 'mcv labs', 'hydroxyurea', 'hemoglobin labs')),
          output = 'median_site_with0s')

make_interactive_squba(grph)

```

# Median without 0s
## All Domains
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_exp_cs_r5') %>% collect(),
          output = 'median_site_without0s')

make_interactive_squba(grph)

```
## Labs + Hydroxyurea
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_exp_cs_r5') %>% collect() %>%
            filter(domain %in% c('anc labs', 'mcv labs', 'hemoglobin labs', 'hydroxyurea')),
          output = 'median_site_without0s')

make_interactive_squba(grph)

```
:::

### Multi Site, Anomaly Detection, Cross-Sectional

:::{.panel-tabset}
# All Visits
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_cs_r5') %>% collect(),
          visit_filter = 'all')

make_interactive_squba(grph)

```
# Inpatient Visits
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_cs_r5') %>% collect(),
          visit_filter = 'inpatient')

make_interactive_squba(grph)

```
# ED Visits
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_cs_r5') %>% collect(),
          visit_filter = 'emergency department')

make_interactive_squba(grph)

```
# Hematology Visits
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_cs_r5') %>% collect(),
          visit_filter = 'hematology specialists')

make_interactive_squba(grph)

```
:::

### Multi Site, Anomaly Detection, Longitudinal

:::{.panel-tabset}
# All Visits

:::{.panel-tabset}
# Procedures
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'all',
                  domain_filter = 'procedures')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Drugs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'all',
                  domain_filter = 'all drugs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Prescription Drugs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'all',
                  domain_filter = 'prescription drugs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Diagnoses
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'all',
                  domain_filter = 'diagnoses')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Labs (All)
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'all',
                  domain_filter = 'all labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# ANC Labs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'all',
                  domain_filter = 'anc labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# MCV Labs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'all',
                  domain_filter = 'mcv labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Hemoglobin Labs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'all',
                  domain_filter = 'hemoglobin labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Hydroxyurea
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'all',
                  domain_filter = 'hydroxyurea')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

:::

# Inpatient Visits
:::{.panel-tabset}
# Procedures
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'inpatient',
                  domain_filter = 'procedures')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Drugs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'inpatient',
                  domain_filter = 'all drugs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Prescription Drugs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'inpatient',
                  domain_filter = 'prescription drugs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Diagnoses
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'inpatient',
                  domain_filter = 'diagnoses')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Labs (All)
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'inpatient',
                  domain_filter = 'all labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# ANC Labs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'inpatient',
                  domain_filter = 'anc labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# MCV Labs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'inpatient',
                  domain_filter = 'mcv labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Hemoglobin Labs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'inpatient',
                  domain_filter = 'hemoglobin labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Hydroxyurea
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'inpatient',
                  domain_filter = 'hydroxyurea')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

:::

# ED Visits
:::{.panel-tabset}
# Procedures
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'emergency department',
                  domain_filter = 'procedures')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Drugs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'emergency department',
                  domain_filter = 'all drugs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Prescription Drugs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'emergency department',
                  domain_filter = 'prescription drugs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Diagnoses
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'emergency department',
                  domain_filter = 'diagnoses')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Labs (All)
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'emergency department',
                  domain_filter = 'all labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# ANC Labs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'emergency department',
                  domain_filter = 'anc labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# MCV Labs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'emergency department',
                  domain_filter = 'mcv labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Hemoglobin Labs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'emergency department',
                  domain_filter = 'hemoglobin labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Hydroxyurea
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'emergency department',
                  domain_filter = 'hydroxyurea')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

:::

# Hematology Visits
:::{.panel-tabset}
# Procedures
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'hematology specialists',
                  domain_filter = 'procedures')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Drugs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'hematology specialists',
                  domain_filter = 'all drugs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Prescription Drugs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'hematology specialists',
                  domain_filter = 'prescription drugs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Diagnoses
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'hematology specialists',
                  domain_filter = 'diagnoses')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Labs (All)
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'hematology specialists',
                  domain_filter = 'all labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# ANC Labs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'hematology specialists',
                  domain_filter = 'anc labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# MCV Labs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'hematology specialists',
                  domain_filter = 'mcv labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Hemoglobin Labs
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'hematology specialists',
                  domain_filter = 'hemoglobin labs')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

# Hydroxyurea
```{r}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la_r5') %>% collect(),
                  visit_filter = 'hematology specialists',
                  domain_filter = 'hydroxyurea')

make_interactive_squba(grph[[1]])
make_interactive_squba(grph[[3]])
```

:::
:::

## Expected Variables Present

### Multi Site, Exploratory, Cross-Sectional
```{r, fig.width=8}

evp_output(process_output = results_tbl('evp_ms_exp_cs_r5') %>% collect(),
           output_level = 'patient')

```
