---
title: "SCA SSDQA Round 3"
format: 
  html:
    toc: true
    toc-location: left
    html-table-processing: none
    embed-resources: true
---

```{r setup, include=FALSE}

library(squba.gen)
library(squba)
# library(gtsummary)
library(gt)
library(patchwork)
library(ggiraph)
library(ggplot2)

setwd(here::here())
source('setup/setup.R')

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

set_argos_default(postgres_session)

```

# Source and Concept Vocabularies

## Multi Site, Exploratory, Cross-Sectional

### Hematology String Search

Searched for the following in the `measurement_source_value` field: `hemoglobin s`, `beta globin`, `hemoglobin identification`, `hemoglobin quant`, or `hemoglobin elect`

```{r}

scv_output(process_output = results_tbl('scv_ms_exp_cs_r3_heme') %>%
             collect(),
           code_type = 'source',
           vocab_tbl = vocabulary_tbl('concept')) %>% gt::sub_missing()

```

### Unmapped Labs

Source values associated with unmapped labs

```{r}

scv_output(process_output = results_tbl('scv_ms_exp_cs_r3_labs') %>%
             collect(),
           code_type = 'cdm',
           vocab_tbl = vocabulary_tbl('concept')) %>% gt::sub_missing()

```

### Unmapped Specialties

Source values associated with unmapped specialties

#### Provider Specialties

```{r}

scv_output(process_output = results_tbl('scv_ms_exp_cs_r3_pv') %>%
             collect(),
           code_type = 'cdm',
           vocab_tbl = vocabulary_tbl('concept')) %>% gt::sub_missing()

```

#### Care Site Specialties

```{r}

scv_output(process_output = results_tbl('scv_ms_exp_cs_r3_cs') %>%
             collect(),
           code_type = 'cdm',
           vocab_tbl = vocabulary_tbl('concept')) %>% gt::sub_missing()

```

# Patient Facts

Limiting to just ANC and MCV labs

```{r}

read_codeset('input_pf_visits', 'ic') %>% 
  pivot_wider(names_from = visit_type,
              values_from = visit_concept_id) %>%
  mutate(`hematology specialists` = 'any visit_concept_id with a hematology provider or care site specialty') %>%
  gt::gt() %>%
  tab_header('Visit Type Definitions') %>%
  opt_stylize(style = 2)

```

## Multi Site, Exploratory, Cross-Sectional

:::{.panel-tabset}

# Median with 0s

```{r, fig.width=8}

grph <- pf_output(process_output = results_tbl('pf_ms_exp_cs') %>% 
                    collect() %>% filter(domain %in% c('anc labs',
                                                       'mcv labs')),
                  output = 'median_site_with0s')

grph

```

# Median without 0s

```{r, fig.width=8}

grph <- pf_output(process_output = results_tbl('pf_ms_exp_cs') %>% 
                    collect() %>% filter(domain %in% c('anc labs',
                                                       'mcv labs')),
                  output = 'median_site_without0s')

grph

```

:::

## Multi Site, Anomaly Detection, Longitudinal

### Inpatient

:::{.panel-tabset}

# ANC Labs

```{r, fig.width=9, fig.height=8}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la') %>% collect(),
                  output = 'median_site_without0s',
                  visit_filter = 'inpatient',
                  domain_filter = 'anc labs')


grph1 <- grph[[1]] + ggtitle('')
grph2 <- grph[[3]] + ggtitle('')

combo_plot <- grph1 + grph2 + 
  plot_annotation(title = 'Inpatient Visits with ANC Labs') +
  plot_layout(heights = c(5,5))
combo_plot

```

# MCV Labs

```{r, fig.width=9, fig.height=8}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la') %>% collect(),
                  output = 'median_site_without0s',
                  visit_filter = 'inpatient',
                  domain_filter = 'mcv labs')


grph1 <- grph[[1]] + ggtitle('')
grph2 <- grph[[3]] + ggtitle('')

combo_plot <- grph1 + grph2 + 
  plot_annotation(title = 'Inpatient Visits with MCV Labs') +
  plot_layout(heights = c(5,5))
combo_plot

```

:::

### Outpatient

:::{.panel-tabset}

# ANC Labs

```{r, fig.width=9, fig.height=8}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la') %>% collect(),
                  output = 'median_site_without0s',
                  visit_filter = 'outpatient',
                  domain_filter = 'anc labs')


grph1 <- grph[[1]] + ggtitle('')
grph2 <- grph[[3]] + ggtitle('')

combo_plot <- grph1 + grph2 + 
  plot_annotation(title = 'Outpatient Visits with ANC Labs') +
  plot_layout(heights = c(5,5))
combo_plot

```

# MCV Labs

```{r, fig.width=9, fig.height=8}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la') %>% collect(),
                  output = 'median_site_without0s',
                  visit_filter = 'outpatient',
                  domain_filter = 'mcv labs')


grph1 <- grph[[1]] + ggtitle('')
grph2 <- grph[[3]] + ggtitle('')

combo_plot <- grph1 + grph2 + 
  plot_annotation(title = 'Outpatient Visits with MCV Labs') +
  plot_layout(heights = c(5,5))
combo_plot

```

:::

### Outpatient (non-9202)

:::{.panel-tabset}

# ANC Labs

```{r, fig.width=9, fig.height=8}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la') %>% collect(),
                  output = 'median_site_without0s',
                  visit_filter = 'outpatient (non-9202)',
                  domain_filter = 'anc labs')


grph1 <- grph[[1]] + ggtitle('')
grph2 <- grph[[3]] + ggtitle('')

combo_plot <- grph1 + grph2 + 
  plot_annotation(title = 'Non-9202 Outpatient Visits with ANC Labs') +
  plot_layout(heights = c(5,5))
combo_plot

```

# MCV Labs

```{r, fig.width=9, fig.height=8}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la') %>% collect(),
                  output = 'median_site_without0s',
                  visit_filter = 'outpatient (non-9202)',
                  domain_filter = 'mcv labs')


grph1 <- grph[[1]] + ggtitle('')
grph2 <- grph[[3]] + ggtitle('')

combo_plot <- grph1 + grph2 + 
  plot_annotation(title = 'Non-9202 Outpatient Visits with MCV Labs') +
  plot_layout(heights = c(5,5))
combo_plot

```

:::

### Emergency Department
:::{.panel-tabset}

# ANC Labs

```{r, fig.width=9, fig.height=8}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la') %>% collect(),
                  output = 'median_site_without0s',
                  visit_filter = 'emergency department',
                  domain_filter = 'anc labs')


grph1 <- grph[[1]] + ggtitle('')
grph2 <- grph[[3]] + ggtitle('')

combo_plot <- grph1 + grph2 + 
  plot_annotation(title = 'ED Visits with ANC Labs') +
  plot_layout(heights = c(5,5))
combo_plot

```

# MCV Labs

```{r, fig.width=9, fig.height=8}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la') %>% collect(),
                  output = 'median_site_without0s',
                  visit_filter = 'emergency department',
                  domain_filter = 'mcv labs')


grph1 <- grph[[1]] + ggtitle('')
grph2 <- grph[[3]] + ggtitle('')

combo_plot <- grph1 + grph2 + 
  plot_annotation(title = 'ED Visits with MCV Labs') +
  plot_layout(heights = c(5,5))
combo_plot

```

:::

### Hematology Specialist

:::{.panel-tabset}

# ANC Labs

```{r, fig.width=9, fig.height=8}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la') %>% collect(),
                  output = 'median_site_without0s',
                  visit_filter = 'hematology specialists',
                  domain_filter = 'anc labs')


grph1 <- grph[[1]] + ggtitle('')
grph2 <- grph[[3]] + ggtitle('')

combo_plot <- grph1 + grph2 + 
  plot_annotation(title = 'Hematology Specialist Visits with ANC Labs') +
  plot_layout(heights = c(5,5))
combo_plot

```

# MCV Labs

```{r, fig.width=9, fig.height=8}

grph <- pf_output(process_output = results_tbl('pf_ms_anom_la') %>% collect(),
                  output = 'median_site_without0s',
                  visit_filter = 'hematology specialists',
                  domain_filter = 'mcv labs')


grph1 <- grph[[1]] + ggtitle('')
grph2 <- grph[[3]] + ggtitle('')

combo_plot <- grph1 + grph2 + 
  plot_annotation(title = 'Hematology Specialist Visits with MCV Labs') +
  plot_layout(heights = c(5,5))
combo_plot

```

:::