---
title: "SCA SSDQA Round 8"
format: 
  html:
    toc: true
    toc-location: left
    html-table-processing: none
    embed-resources: true
---

```{r setup, include=FALSE}

library(squba.gen)
library(squba)
library(gtsummary)
library(gt)
library(patchwork)
library(ggiraph)
library(ggplot2)

setwd(here::here())
source('setup/setup.R')

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

set_argos_default(postgres_session)

```

## Expected Variables Present

These results are reflecting the proportion of hydroxyurea rows in drug_exposure that have non-null associated metadata values. 

### Multi Site, Exploratory, Cross-Sectional

```{r}

plt <- evp_output(process_output = results_tbl('evp_ms_exp_cs_r8') %>%
                    collect(),
                  output_level = 'row')

make_interactive_squba(plt)

```

### Multi Site, Exploratory, Longitudinal

```{r}

plt <- evp_output(process_output = results_tbl('evp_ms_exp_la_r8') %>%
                    collect(),
                  output_level = 'row',
                  filter_variable = c('days_supply', 'refills'))

plt2 <- evp_output(process_output = results_tbl('evp_ms_exp_la_r8') %>%
                    collect(),
                  output_level = 'row',
                  filter_variable = c('quantity', 'frequency'))

make_interactive_squba(plt)
make_interactive_squba(plt2)

```

## Quantitative Variable Distribution

`frequency` is a character field, so it has been excluded here.

### Multi Site, Exploratory, Cross-Sectional

```{r}

qvd_output(process_output = results_tbl('qvd_ms_exp_cs_r8') %>% collect(),
           display_outliers = TRUE)

```

```{r}

qvd_output(process_output = results_tbl('qvd_ms_exp_cs_r8') %>% collect(),
           display_outliers = FALSE)

```

### Multi Site, Exploratory, Longitudinal

```{r}

plt <- qvd_output(process_output = results_tbl('qvd_ms_exp_la_r8') %>% collect(),
                  summary_stat = 'median')

make_interactive_squba(plt)

```